RadLib: a radiative property model library for combustion CFD

### 2021-07-19 submissions/CPC_response_to_reviewers.md

## Reviewer 1

This manuscript introduces “RadLib,” a C++ library to calculate absorption coefficients for use in radiative heat transfer calculations. The library has reasonable value to the research community, despite a few limitations in its scope and design. The library is self-contained (doesn’t have any external dependencies), which is convenient.

I have a number of comments on the manuscript as well as the software itself which the authors should consider to improve the manuscript and software.

**The authors thank the reviewer for their time and careful review.**

@@

### Manuscript:

1. There is no general user documentation provided in section 3. Figure 1 includes information that is more algorithmic than illustrative of the API.

	**Section 3 has been significantly revised and extended to include more information on how users can include and interact with the RadLib library. This includes a description of the build procedure and a list of installed files. Compilation of user code with RadLib is outline. A description of the interface functions is also provided. The key interface function was ```get_k_a(...)```. An additional function is now included and described, ```get_k_a_oneband(...)```. The function arguments are now described. Since the initial submission, a Fortran 90 interface has been added and this is included in the section.**

2. Section 5 makes several editorial claims that are quite subjective, and not well-supported:
	1. First sentence: “historically difficult to implement … complexity and high computational costs”
		- Property evaluation is not the expensive part of a radiation calculation. Solving the RTE is the expensive part.
        	- I wouldn’t characterize the property evaluation as particularly complex in comparison with other aspects of combustion simulations (kinetics, thermodynamics, transport properties).

@@

    2. At the end of the first paragraph, the authors seem to imply that RadLib will solve the challenges of radiation modeling. Again, it is the RTE solver, not the property evaluation, that is the largest time-sink in terms of computer and human resources.

    3. These kinds of statements persist throughout the second paragraph as well. There are limitations in RadLib such as lack of scattering treatment for particle-laden flows, inability to include more species, lack of any line-by-line capabilities, etc. The library checks a few useful boxes, but the verbiage here seems to take more credit than the authors may be due.

    **In the first sentence and paragraph of Section 5, "radiative heat transfer models" does not refer specifically to either radiation property models or RTE evaluation methods, but the treatment of computational radiative heat transfer as a whole. This generalization was intended for the entire first paragraph of Section 5.**

    **Regarding solution of the RTE versus the radiative property model, the reviewer is correct that in most engineering calculations, specification and implementation of the RTE can be more complex and costly than that of the property model. For both parts, however, this depends strongly on the particular model used, (and the geometry considered). The optically-thin model RTE model is trivial, and the RCSLW property model is not. We revised the manuscript to include a discussion of this in the second paragraph of the introduction, with a specific note that "In practical engineering simulations, the solution of the RTE is often the most complex and costly part of radiative simulation..." That said, we believe that access to good radiative property models as presented in this paper is a valuable contribution.**

    **We want to be careful with what is claimed in the paper, and some major revision has occurred in response to this reviewer's comments and others. Section 4 contained examples provided along with results, but now contains a description of the examples provided with the code. Section 5 contained some discussion items as noted by the reviewer, but now includes simulation results for the examples along with a CFD demonstration. The discussion items noted by the reviewer have been modified and folded into the Conclusions section.
    **

@@

3. Section 5 claims that “RadLib’s modular framework is designed to easily accommodate new models as well,” which is a bit of an overstatement. See comments below w.r.t. assumptions on species considered, hard-coded polynomial coefficients, etc. all of which reduce extensibility.

    **We have reworded this to "...but its design and C++, Python, and Fortran interfaces permit expansion to additional property models." We remove the word "modular" throughout the paper. We do believe that the library can be easily extended. The reviewer is correct that we do not provide explicit functionality, for, e.g., generic extension to other species. In some cases, like the PM model, such extension would be trivial within the existing code structure. In the RCSLW model, extension to other species would require provision of the species ALBDF, and then extension would be a straightforward extension of the code, but the code is not set up for arbitrary species in arbitrary order. The library is primarily targeted at combustion applications where CO2 and H2O are the primary radiative species. Future efforts may motivate further extension.

@@

4. There are several minor issues that need to be addressed: 
	1. Abstract: “well-written” is subjective and should be removed.

		**Done.**

	2. Introduction: second sentence: “Combustion simulations…” is a run-on sentence.

    **We have reworded the sentence to "For example, combustion simulations are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost."**

@@

		**Fixed section heading. Now correctly reads "Declaration of Competing Interests".**

### Software deficiencies & suggestions:

1. API doxygen documentation is non-standard. It appears that the doxygen documentation is provided in the .cc files rather than the header files, which is where it is typically found. Downstream developers would typically be working from headers and the installed library, so it is convention to have doxygen documentation in the header only. This also reduces clutter in the implementation files.

**We believe this to be a stylistic preference. The reviewer's argument makes more sense for libraries that are distributed without the source. In our case, we provide the source and the header files. We follow the approach of putting class comments, data member documentation, and class usage in the header, and documentation of how the methods/functions work in the source files where they are defined. This has the benefit of not cluttering the header files. There certainly is precedence for this in online discussions. Here's a quote from the [doxygen website](https://www.doxygen.nl/manual/docblocks.html): "Unlike most other documentation systems, doxygen also allows you to put the documentation of members (including global functions) in front of the definition. This way the documentation can be placed in the source file instead of the header file. This keeps the header file compact, and allows the implementer of the members more direct access to the documentation." Furthermore, Doxygen is primarily used to build external documentation (html), so, from that perspective, it does not seem as important where the Doxygen comments are in the source code.**

@@

2. make_examples.sh:
    1.	will only work with a g++ compiler in the user’s path.
    1.	Is referred to as build_examples.sh in the README.md file
    1.	is redundant with the cmake build system and isn’t portable. It should probably be removed.

	**The ```make_examples.sh``` file has been removed and examples are built with CMake. This script was originally included for reference.**

@@

3. It appears that there are no tests associated with the library. This is a bit surprising - I would expect regression test coverage on the basic API functionality.

    **The API is pretty simple and consists of two functions. Extensive examples are provided, which are compared to LBL data, and which, as published here, are identical to the results of the published radiation models.**

<!--
	**The authors acknowledge the lack of tests associated with the library and note that basic test coverage is currently being developed.**
-->

@@

5. CMake build system:
    1.	Consider installing a “RadLib.cmake” file for downstream usage by CMake-based projects. This helps downstream build systems configure for RadLib usage (setting include paths, etc.).

		**This is a good point. The installation now includes ```radlib.cmake``` files, located by default in the ```installed/cmake/``` directory, for downstream usage.**

@@

    3.	probably shouldn’t specify optimize or debug flags directly, as CMake will provide appropriate values on most platforms.

		**The CMake build has been updated to reflect this.**

    3.	the default build type isn’t defaulting to Release for me; it remains blank.

        **This appears to be working in the revised version of the code. Testing shows the value of CMAKE_BUILD_TYPE as set to Release if not otherwise set. This is specified at the very top of the base CMakeLists.txt file. Note that the build type can be overridden by IDE build settings, among other things, and that this may be a system issue specific to the reviewer.**

@@

    5.	I suggest not using verbose makefiles by default.

  		**The build has be updated so that verbose makefiles are no longer the default.**

@@

    3.	Using GLOB to install the headers is not the appropriate CMake approach.

		**The build updated accordingly; GLOB is no longer used to install header files.**

@@

    5.	the data files are not copied into the examples build directory, meaning that the example executables do not run.

        **The original code has been updated and tested and this does not appear to be an issue.**

@@

    7.	The run-examples.sh script is not helpful as it is not installed into the build directory where the executables are produced and doesn’t have path information to actually run the executables.

		**Executables for the examples are installed within the example folders (in addition to the build directories), so ```run_examples.sh``` runs without any issues.**

@@

    3.	Using “doxygen” as a target is not ideal since it conflicts with the “doxygen” executable name. It still works fine though...

		**Build target name has been changed from "doxygen" to "docs" for safety. Note that building the documentation is off by default.**

@@

5. It appears that line-by-line data from HITEMP/HITRAN files cannot be loaded into RadLib. That’s an unfortunate limitation, but not a deal-breaker.

    **This is true. The code is not presently set up to load HITEMP/HITRAN data. This is a good suggestion and we plan to extend the model to allow LBL simulations in the future.**

@@

6. It looks like the software hard-codes Plank mean absorption coefficients as (fourth-order?) polynomial fits? Same for WSGG. There is no discussion of why this was chosen, how the coefficients were determined, or a characterization of its accuracy. Do you observe any problematic behavior with the fourth order polynomials over temperatures from 300 to 3000 K?  Are these interpolants or regression of data?

    **The software implements the PM and WSGG models as provided in the cited references, which use polynomial fits. Model details are noted in the cited references. Use of a polynomial fit is standard for WSGG models, and a polynomial fit to temperature for species for the PM model seems reasonable. The PM model used is the one advocated by the TNF workshop cited in the paper, which is standard in the combustion community. The temperature range is 300-2500 K for the PM model. This is now stated in the paper, and the code enforces this range. The range for the WSGG model is 300-2400 K. The range for the RCSLW model is 300-3000 K. Temperatures outside these bounds use these bounds for the WSGG and RCSLW models. This is now stated in the paper.**

@@

7. The two previous items combined lead to a significant limitation of RadLib: one cannot easily add new species or modify existing data that is used to generate the absorption coefficients since there has been internal preprocessing of (an unknown subset of) the HITEMP/HITRAN databases to produce curve fits. And given that this process is opaque, it isn’t reproducible.

    **The implemented models are not opaque, they come from the literature. The novelty of the presented library is not the development of the absorption models, but the implementation, validation, and documentation of a library for application. Using radlib to generate correlations for species using HITEMP/HITRAN is outside of the intended scope. We acknowledge that extra work is required to extend the models to additional species, or to extend the temperature ranges. However, the species included cover a very wide range of practical applications, certainly in the combustion field, and models for other species (e.g., for WSGG, and RCSLW) are often not available. Indeed, Bordbar's WSGG model is one of the few (if not the only one) that is provided for arbitrary compositions of CO2 and H2O, with others assuming fixed or limited ratios. That said, radlib is documenented and while the code does not provide extension machinery directly, extending to additional species by following the existing code structure would not be difficult if such data/correlations were available.**

@@

8. RadLib only considers CO2 and H2O for WSGG, which is fairly limited. Even for Plank mean, only H2O, CO2, CO and CH4 are considered. NO and OH would be nice to include. It appears that including additional species would be a non-trivial undertaking.

    **See our reply to the previous comment regarding additional species. For heat transfer applications in combustion, NO and OH are minor species and will not contribute in any meaningful way. CO2, H2O, and soot will drive the radiation in practical configurations. It would be nice to include CO in the WSGG model, and we would like to do this following Bordbar's approach. But even CO is a minor species compared to CO2, both in terms of its concentration in practical systems (usually), and it's asorption coefficient on an equal concentration basis. CH4 was only included in the PM model from the TNF workshop since many of the fuels used there include CH4. But CH4 will largely be present at relatively low temperatures, not the highly radiating flame zones.**

	**We note that major revisions have been made to the paper text to clarify points like these for readers who do not specialize in combustion processes or modeling and provide additional information about why these models were chosen for implementation in RadLib.**

@@

9. Documentation:
    1.	Generating the documentation directly via doxygen v. 1.8.20 gives numerous warnings about obsolete tags and then fails because it is looking for a relative path “../../docs/doxygen” that doesn’t exist. This should be fixed.
    1.	Generating the doxygen documentation via the build system target (“make doxygen”) does seem to work fine.

	**The build process has been updated so that documentation can be generated by the system target or manually by running the command ```doxygen``` in the docs folder.**

----------------------------------------------------

### 2021-07-19 manuscript/manuscript.tex
DOL: reviewer 1 responses finished, with corresponding checks of the paper and code. The paper will need to be gone through and edited still.

%% This list environment is used for the references in the
%% Program Summary
%%
\usepackage{lineno}
\usepackage{amsmath}
\usepackage{float}
\usepackage[version=4]{mhchem}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{bm}

@@

\begin{abstract}
RadLib is a modular C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations. RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its modular design and C++ and Python interface options permit convenient expansion to additional models. Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions. The computational cost of the models is also compared. RadLib provides researchers with convenient access to validated radiation property models and a framework for further development. 
\end{abstract}

@@

The core mechanisms of radiative phenomena are physically and mathematically complex. Unlike other modes of heat transfer, radiation is governed by a set of integro-differential equations that depend on both direction and wavelength, known as the radiative transfer equations (RTE). Computational radiation solvers require two distinct but interconnected parts: (1) a solution approach for the radiative transfer equations (RTE) and (2) a radiation property model. RadLib addresses the second part by providing a set of implemented and validated radiation property models that can be applied to various solution approaches for the RTE.

@@

With RadLib, we aim to provide researchers with a convenient access point for radiative property models that can be interfaced with various RTE solution approaches suitable for CFD applications. RadLib is a modular C++ library with an optional Python interface. Currently, RadLib only calculates radiation absorption coefficients and weighting factors for use in global radiation models, but expansion to other radiative properties and model types is possible. Three models are fully implemented and validated. All models use a common interface to facilitate researchers' access to and use of radiation modeling tools suitable for combustion CFD applications.

@@

The specific correlations for the Planck Mean absorption coefficients generated by RadLib come from the Turbulent Nonpremixed Flame (TNF) Workshop, an ongoing collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}. These particular correlations were chosen for RadLib's PM model because of the popularity and widespread use of the TNF Workshop radiation model in combustion research despite its notable limitations. Its temperature-dependent correlations are based on the RADCAL database \citep{Grosshandler_1993}, which has been largely superseded by more comprehensive and accurate databases, particularly HITRAN and HITEMP \citep{Rothman_2010}. TNF Workshop literature shows that in cases where the optically thin approximation accurately describes the system, such as in simple hydrogen jet flames, the PM model produces accurate results \citep{Barlow_1999}. In cases where the optically thin assumption is not reasonable, however, including most practical combustion scenarios of interest to scientists and engineers, the PM model does not produce accurate results, overpredicting radiative heat loss and underpredicting flame temperature by 100$^{\circ}$ or more \cite{Frank_2000,Zhu_2002,Coelho_2002}.

@@

Weighted sum of gray gases (WSGG) models generate radiation absorption coefficients for use with the spectrally integrated RTE (Eq.~\ref{e:RTE_wsgg}).
RadLib implements the WSGG model presented by Bordbar et al. \citep{Bordbar_2014,Bordbar_2020}, which uses correlations based on the HITEMP 2010 database \cite{Rothman_2010}. It models mixtures of gaseous \ce{CO2} and \ce{H2O}, the two most significant radiatively participating species in most combustion environments, using four gray gases and one clear gas. Absorption coefficients are calculated by 
%
\begin{linenomath}
\begin{equation}
    \kappa_j=\sum_{k=0}^{4}d_{j,k}M_r^k,
\end{equation}
\end{linenomath}
%
where $\kappa_j$ is the absorption coefficient for gray gas $j$, $d_{j,k}$ is a correlated model coefficient, and $M_r$ is the molar ratio $y_{\mathrm{H_2O}}/y_{\mathrm{CO_2}}$. The weight factors are calculated by 
%
\begin{linenomath}
\begin{equation}
    a_j=\sum_{k=0}^{4}b_{j,k}T_r^k,
\end{equation}
\end{linenomath}
%
where $a_j$ is the weighting factor for gas $j$ and $T_r$ is a scaled temperature equal to $T/T_{ref}$ with $T_{ref}=1200$K. The value of $b_{i,j}$ is calculated by 
%
\begin{linenomath}
\begin{equation}
 b_{j,k}=\sum_{i=0}^{4}C_{j,k,i}M_r^i,
\end{equation}
\end{linenomath}
%
where $C_{j,k,i}$ is another correlated model coefficient. The model coefficients $d_{j,k}$ and $C_{j,k,i}$ are provided by Bordbar et~al. \citep{Bordbar_2014,Bordbar_2020}.

@@

The ALBDF data for \ce{H2O}, \ce{CO2}, and \ce{CO}---valid for pressures between 0.1 atm and 50 atm and temperatures between 300 K and 3000 K---are provided by Pearson et al. \cite{Pearson_2014} and can be accessed in both correlated and tabulated form at \cite{Solovjov_2014b}. RadLib uses the tabulated data coupled with multilinear interpolation; both the tabulated data and the multilinear interpolator are included with the RadLib package as part of the RCSLW method.

@@

The code installation folder includes directories \texttt{include} containing header files and a Fortran module file, 
\texttt{lib} containing library files for each interface, and \texttt{rcslw\textunderscore data} containing binary data files used by the RCSLW model. These binary files contain the ALBDF functions for a given species at a given pressure (in atm units), as indicated by the file name. The \texttt{include} directory contains the following interface header and module (Fortran) files:
%
\begin{itemize}
    \item \texttt{rad\textunderscore planck\textunderscore mean.h},
    \item \texttt{rad\textunderscore wsgg.h},
    \item \texttt{rad\textunderscore rcslw.h},
    \item \texttt{rad\textunderscore module.mod}.
\end{itemize}
%
The C++ and Fortran libraries in the \texttt{lib} folder are
\begin{itemize}
    \item \texttt{libradlib.a},
    \item \texttt{libradlib\textunderscore fortran.a},
\end{itemize}
%
This folder also contains the Python module.
The code installation additionally generates a relocatable CMake package for downstream usage, located at \texttt{build/cmake/radlib/radlib.cmake}. If the Python interface is built, the location of the installed Python package needs to be added to the \texttt{PYTHONPATH} environment variable. A command to do this is provided at the end of the installation, for example, \\ {\scriptsize \texttt{export PYTHONPATH="/home/user/radlib/installed/lib/python3.8/site-packages:\$PYTHONPATH"}}.

@@

Radiative heat transfer phenomena are historically difficult to model and implement in CFD calculations due to their high level of conceptual and mathematical complexity and potentially large computational cost. The vast majority of combustion CFD studies either neglect radiative heat transfer modeling or employ oversimplified models that do not accurately represent combustion systems. Most combustion processes of interest to engineers and researchers, however, involve significant radiative heat transfer, and simulations require robust radiative modeling, which includes both radiation property modeling and solution approaches for the radiative transfer equation, to yield accurate results.

We presented RadLib, a C++ library of radiation property models developed to ease some of the obstacles and reduce the complexity inherent to the process of implementing radiative property models in CFD simulations. At present, it includes three major radiation property models---Planck Mean (PM) absorption coefficients using the optically thin approximation, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its modular design and C++ and Python interfaces permit expansion to additional property models. Each of the implemented models has been validated and the library's structure and functionality has been outlined.

@@

RadLib is intended as a convenient access point for researchers who require radiation property modeling tools for combustion CFD, but could potentially be applied to research problems involving radiative heat transfer in a variety of other fields as well. RadLib is designed to facilitate and simplify the process of implementing and/or using radiative property models; it consolidates various model types into a single extensible library with a consistent framework, reducing some of the overhead associated with choosing,  implementing, and testing radiation property models. Its framework can be used to implement and validate new models as well as compare existing models under consistent conditions. By facilitating model comparison through a common interface, RadLib can provide a practical means of testing specific modeling approaches without the restrictions imposed by large-scale CFD simulations. With RadLib, we believe that researchers will be able to put more of their time and effort into meaningful results rather than code or model development for radiative heat transfer in combustion CFD.

>>>>

%% This list environment is used for the references in the
%% Program Summary
%%
\usepackage{lineno}
\usepackage{amsmath}
\usepackage{float}
\usepackage[version=4]{mhchem}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{bm}
\usepackage{seqsplit}

@@

\begin{abstract}
RadLib is a C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations. RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its design and C++ and Python interface options permit convenient expansion to additional models. Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions. The computational cost of the models is also compared. RadLib provides researchers with convenient access to validated radiation property models and a framework for further development. 
\end{abstract}

@@

The core mechanisms of radiative phenomena are physically and mathematically complex. Unlike other modes of heat transfer, radiation is governed by a set of integro-differential equations that depend on both direction and wavelength, known as the radiative transfer equations (RTE). Computational radiation solvers require two distinct but interconnected parts: (1) a solution approach for the radiative transfer equations (RTE) and (2) a radiation property model. 
Complexity, implementation, and computational costs of these two parts can vary widely, depending on the models chosen. The optically thin model for solution of the RTE is trivial, while the discrete ordinates model (DOM) and Reverse Monte Carlo Ray Tracing (RMCRC) model, among others, are significantly more involved. Similarly for radiation property models, which range from simple correlations for mean absorption coefficients, to gray gas models such as the weighted sum of gray gas model (WSGG), to the more advanced Spectral Line WSGG (SLW) family of model, to full line-by-line (LBL) approaches. In practical engineering simulations, the solution of the RTE is often the most complex and costly part of radiative simulation, but advanced property models, such as the Rank Correlated SLW (RCSLW), discussed here, are nontrivial models to understand, implement, and validate.
RadLib addresses this second, radiative property model part of radiative simulation by providing a set of implemented and validated radiation property models that can be applied to various solution approaches for the RTE.

@@

With RadLib, we aim to provide researchers with a convenient access point for radiative property models that can be interfaced with various RTE solution approaches suitable for CFD applications. RadLib is a C++ library with an optional Python interface. Currently, RadLib only calculates radiation absorption coefficients and weighting factors for use in global radiation models, but expansion to other radiative properties and model types is possible. Three models are fully implemented and validated. All models use a common interface to facilitate researchers' access to and use of radiation modeling tools suitable for combustion CFD applications.

@@

The specific correlations for the Planck Mean absorption coefficients generated by RadLib come from the Turbulent Nonpremixed Flame (TNF) Workshop, an ongoing collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}. These particular correlations were chosen for RadLib's PM model because of the popularity and widespread use of the TNF Workshop radiation model in combustion research despite its limitations. Its temperature-dependent correlations are based on the RADCAL database \citep{Grosshandler_1993}, which has been largely superseded by more comprehensive and accurate databases, particularly HITRAN and HITEMP \citep{Rothman_2010}. The absorption coefficient correlations use fourth or fifth order polynomial fits in the range 300-2500 K. TNF Workshop literature shows that in cases where the optically thin approximation accurately describes the system, such as in simple hydrogen jet flames, the PM model produces accurate results \citep{Barlow_1999}. In cases where the optically thin assumption is not reasonable, however, including most practical combustion scenarios of interest to scientists and engineers, the PM model does not produce accurate results, overpredicting radiative heat loss and underpredicting flame temperature by 100$^{\circ}$ or more \cite{Frank_2000,Zhu_2002,Coelho_2002}.

@@

Weighted sum of gray gases (WSGG) models generate radiation absorption coefficients for use with the spectrally integrated RTE (Eq.~\ref{e:RTE_wsgg}).
RadLib implements the WSGG model presented by Bordbar et al. \citep{Bordbar_2014,Bordbar_2020}, which uses correlations based on the HITEMP 2010 database \cite{Rothman_2010}. It models mixtures of gaseous \ce{CO2} and \ce{H2O}, the two most significant radiatively participating species in most combustion environments, using four gray gases and one clear gas. Absorption coefficients are calculated by 
%
\begin{linenomath}
\begin{equation}
    \kappa_j=\sum_{k=0}^{4}d_{j,k}M_r^k,
\end{equation}
\end{linenomath}
%
where $\kappa_j$ is the absorption coefficient for gray gas $j$, $d_{j,k}$ is a correlated model coefficient, and $M_r$ is the molar ratio $y_{\mathrm{H_2O}}/y_{\mathrm{CO_2}}$. The weight factors are calculated by 
%
\begin{linenomath}
\begin{equation}
    a_j=\sum_{k=0}^{4}b_{j,k}T_r^k,
\end{equation}
\end{linenomath}
%
where $a_j$ is the weighting factor for gas $j$ and $T_r$ is a scaled temperature equal to $T/T_{ref}$ with $T_{ref}=1200$K. The valid temperature range of the model is 300-2400 K; temperatures outside this range use the value at the respective bound. The value of $b_{i,j}$ is calculated by 
%
\begin{linenomath}
\begin{equation}
 b_{j,k}=\sum_{i=0}^{4}C_{j,k,i}M_r^i,
\end{equation}
\end{linenomath}
%
where $C_{j,k,i}$ is another correlated model coefficient. The model coefficients $d_{j,k}$ and $C_{j,k,i}$ are provided by Bordbar et~al. \citep{Bordbar_2014,Bordbar_2020}.

@@

The ALBDF data for \ce{H2O}, \ce{CO2}, and \ce{CO}---valid for pressures between 0.1 atm and 50 atm and temperatures between 300 K and 3000 K---are provided by Pearson et al. \cite{Pearson_2014} and can be accessed in both correlated and tabulated form at \cite{Solovjov_2014b}. Temperatures outside the stated range use the value at the respective bound. RadLib uses the tabulated data coupled with multilinear interpolation; both the tabulated data and the multilinear interpolator are included with the RadLib package as part of the RCSLW method.

@@

The code installation folder includes directories \texttt{include} containing header files and a Fortran module file, 
\texttt{lib} containing library files for each interface, and \texttt{rcslw\textunderscore data} containing binary data files used by the RCSLW model. These binary files contain the ALBDF functions for a given species at a given pressure (in atm units), as indicated by the file name. The \texttt{include} directory contains the following interface header and module (Fortran) files:
%
\begin{itemize}
    \item \texttt{rad\textunderscore planck\textunderscore mean.h},
    \item \texttt{rad\textunderscore wsgg.h},
    \item \texttt{rad\textunderscore rcslw.h},
    \item \texttt{rad\textunderscore module.mod}.
\end{itemize}
%
The C++ and Fortran libraries in the \texttt{lib} folder are
\begin{itemize}
    \item \texttt{libradlib.a},
    \item \texttt{libradlib\textunderscore fortran.a},
\end{itemize}
%
This folder also contains the Python module.
The code installation additionally generates relocatable CMake files for downstream usage, located at \texttt{\seqsplit{installed/cmake/radlib/radlib.cmake}} and \texttt{\seqsplit{installed/cmake/radlib\textunderscore fortran/radlib\textunderscore fortran.cmake}}, where \texttt{installed/} may be replaced with a user-specified installation path. If the Python interface is built, the location of the installed Python package needs to be added to the \texttt{PYTHONPATH} environment variable. A command to do this is provided at the end of the installation, for example, \texttt{\seqsplit{export\ PYTHONPATH="/home/user/radlib/installed/lib/python3.8/site-packages:\$PYTHONPATH"}}.

@@

Radiative heat transfer phenomena are historically difficult to model and implement in CFD calculations due to their high level of conceptual and mathematical complexity and potentially large computational cost. Many combustion CFD studies either neglect radiative heat transfer modeling or employ oversimplified models that do not accurately represent combustion systems. Most combustion processes of interest to engineers and researchers, however, involve significant radiative heat transfer, and simulations require robust radiative modeling, which includes both radiation property modeling and solution approaches for the radiative transfer equation, to yield accurate results.

RadLib is a C++ library of radiation property models developed to facilitate implementing radiative property models in CFD simulations. At present, it includes three major radiation property models---Planck Mean (PM) absorption coefficients using the optically thin approximation, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its design and C++, Python, and Fortran interfaces permit expansion to additional property models. Each of the implemented models has been validated and the library's structure and functionality has been outlined.

@@

RadLib is intended as a convenient access point for researchers who require radiation property modeling tools for combustion CFD, but could potentially be applied to research problems involving radiative heat transfer in other fields as well. RadLib is designed to facilitate and simplify the process of implementing and/or using radiative property models; it consolidates various model types into a single extensible library with a consistent framework, reducing some of the overhead associated with choosing, implementing, and testing radiation property models. Its framework can be used to implement and validate new models as well as compare existing models under consistent conditions. By facilitating model comparison through a common interface, RadLib can provide a practical means of testing specific modeling approaches without the restrictions imposed by large-scale CFD simulations. With RadLib, we believe that researchers will be able to put more of their time and effort into meaningful results rather than code or model development for radiative heat transfer in combustion CFD.
